XXXXX

### 2014-09-27 paper/paper1.tex
R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS

>>>>

\subsubsection{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS}

\begin{itemize}
	\item see R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
	\item covering approaches: ShEx, SPIN
\end{itemize}

\subsubsection{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}

\begin{itemize}
	\item instances of specific class must not have some object property
  \item OWL 2 DL: ObjectComplementOf ( DataSomeValuesFrom ( DataPropertyExpression rdfs:Literal ) )
	\item covering approaches: ShEx, SPIN
\end{itemize}

constraint (SPIN)

A matching triple has any predicate except those excluded by the '-' operator.

A matching triple has any object except those excluded by the '-' operator.
